Case study: Genome-Wide Association Analyses (GWAS)

### 2018-03-22 datasets/GWAS/GWAS.Rmd
Change results output extension to rds

```{r, GWAS1-sb, results="hide", message=FALSE}
resN <- paste0(resdir, "bmi_N_summarizedBenchmark_",
               nrow(bmi), ".RData")

duration <- NA
if (!file.exists(resN)) {
  t1 <- proc.time()
  sbN <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_N)), 
                          ftCols = c("ind_covar_N"),
                          parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sbN)$data_download_link <- 
    "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  saveRDS(sbN, file=resN)
  duration <- round((proc.time()-t1)[3]/60,1)
}else{
  sbN <- readRDS(resN)
}
```

@@

```{r, GWAS1-sb2, results="hide", message=FALSE}
resAF <- paste0(resdir, "bmi_AF_summarizedBenchmark_",
nrow(bmi), ".RData")

duration <- NA
if (!file.exists(resAF)){
  t1 <- proc.time()
  sbAF <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_AF) %>%
                                  filter(!is.na(ind_covariate))), 
                            ftCols = c("ind_covar_AF"),
                            parallel=TRUE, BPPARAM=multicoreParam)
  metadata(sbAF)$data_download_link <-    
    "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
  saveRDS(sbAF, file=resAF)
  duration <- round((proc.time()-t1)[3]/60,1)
}else{
  sbAF <- readRDS(resAF)
}
```

```{r, echo=FALSE}
if(!is.na(duration)){
  message("This step took ", duration, " minutes for ", nrow(bmi), " SNPs using ",
  cores, " cores.")
}
```

>>>>

```{r, GWAS1-sb, results="hide", message=FALSE}
resN <- file.path(resdir, paste0("bmi_N_summarizedBenchmark_", nrow(bmi), ".rds"))

duration <- NA
if (!file.exists(resN)) {
    t1 <- proc.time()
    sbN <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_N)), 
                             ftCols = c("ind_covar_N"),
                             parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sbN)$data_download_link <- 
                    "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
    saveRDS(sbN, file=resN)
    duration <- round((proc.time()-t1)[3]/60,1)
} else {
    sbN <- readRDS(resN)
}
```

@@

```{r, GWAS1-sb2, results="hide", message=FALSE}
resAF <- file.path(resdir, paste0("bmi_AF_summarizedBenchmark_", nrow(bmi), ".rds"))

duration <- NA
if (!file.exists(resAF)) {
    t1 <- proc.time()
    sbAF <- bd %>% buildBench(data=(bmi %>% mutate(ind_covariate=ind_covar_AF) %>%
                                    filter(!is.na(ind_covariate))), 
                              ftCols = c("ind_covar_AF"),
                              parallel=TRUE, BPPARAM=multicoreParam)
    metadata(sbAF)$data_download_link <-    
                     "http://portals.broadinstitute.org/collaboration/giant/images/3/3a/BMI.SNPadjSMK.zip"
    saveRDS(sbAF, file = resAF)
    duration <- round((proc.time()-t1)[3]/60, 1)
} else {
    sbAF <- readRDS(resAF)
}
```
